\documentclass[12pt,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\begin{document}
\title{BitWatt - Co-ordinating Sustainable Power Generation}
\author{Hugo O'Connor, Bit Trade Labs}
\maketitle
\tableofcontents
\newpage
\section {Status of this Memo}

This document outlines the design for a decentralised collaborative organisation to promote sustainable power generation and requests discussion and suggestions for improvements. Distribution of this memo is unlimited.

\section {Acknowledgements}

The following people contributed the thinking and ideas collected in this document;

\section {Motivation}

Inefficiencies in the Australian retail power market mean residential solar energy producers are getting around 6cents per kiloWatt hour for their output, which is immediately sold back to retail consumers for around 24cents per kiloWatt hour. Individually, residential solar energy producers have limited bargaining power. The Ethereum blockchain provides a mechanism for individual producers to collectively bargain a better price for their output. If we can increase the price paid for sustainably produced energy, we can increase the incentive to produce sustainable energy and grow the green economy.

\section {Background}

Various initiatives to promote renewable energy production have been undertaken by the Australian government.  As the market has grown, technology has improved and prices of solar panels have come down. However, residential solar energy producers have not been able to get a fair price for their contributions to the grid. Power retailers, who benefit from existing market inefficiencies 

\section {Stakeholders}

Stakeholders

Commercial and residential with solar already installed

already in market: transitioning and augmentation
Benefits: better price, up-scaling, maximising
Willing to install (price has scared them off)

newcomer: support to join
Benefits: shortening return on investment, reducing uncertainty
Raising awareness of collective approach

outside market/unaware: education, resources and contacts
Benefits: highlighting opportunities, ways to access and support
Businesses

strata management
small businesses (existing and new)
Carbon credit, renewable energy credits etc
Research and development

sustainable technology research at Western Sydney University
expand as new technology develops e.g. building-attached PVC - building-integrated PVC
Range of potential roles and responsibilities of Empower Parramatta: solar energy generator, retailer, consultant, supplier, maintenance, facility manger, quality assurance (compliance and benchmarks)

Potential test sites (to invite on board as part of funding proposal): public housing (already interest from one organisation), schools (will approach sustainability officer contact at Parra council who works with local schools), council buildings (we have a youth centre contact), stadium, clubs, commercial, residential

Benefits of becoming a test-site: i) better price, up-scaling, maximising, ii) shortening return on investment, reducing uncertainty iii) highlighting opportunities, ways to access and support

\section {Proposed Model}

The proposed solution is to create an intermediary power company, Empower, to act as a retailer, consultant, supplier, maintenance provider, facility manger, and  quality assurance provider. Empower will create smart meter hardware to track contributions into the grid from a distributed set of residential power producers. In exchange for each kWh generated by the residential power producer, Empower will credit the producer with one BitWatt, a crypto-token that can be traded on the open market and redeemed later for 1 kWh of power supplied by Empower.

\section {Technical Considerations}


\end{document}